---
title: "Problem Set 6"
author: "Rebecca Xi"
date: "3/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(infer)
library(gt)
library(ggplot2)
library(tidyverse)
```

## Question 1: Sampling and Confidence Intervals

```{r 1, echo=FALSE}

# Here I write a function, create_deck(), which creates a deck of cards as a
# tibble with 52 rows and four columns: suit, value, points and name. (I list
# the value column first so as to mimic the table in the problem set
# instructions.) The cards are ordered by suit: diamonds, hearts, clubs, spades,
# and go from 2 to Ace within each suit. J, Q, K, and A each have a point value
# of 10, which I set using an ifelse() condition in creating the points column.
# The name column pastes the value and suit, separated by “of".

create_deck <- function() {
  tibble(
    value = rep(c(2:10, "J", "Q", "K", "A"), times = 4),
    points = ifelse(
      value == "J" | value == "K" | value == "Q" | value == "A", 
      10, 
      value
    ),
    suit = rep(c("diamonds", "hearts", "clubs", "spades"), each = 13),
    name = paste(value, suit, sep = " of ")
  )
}

# Here I write a draw_card() function which takes parameters n (how many cards
# to draw) and report (which column to return). First, the function calls
# create_deck() to set up the deck of cards, then calls sample_n() to sample n
# cards from the deck and selects the requested column. I end by calling pull()
# in order to convert the function output from a column to the desired format.

draw_card <- function(n, report) {
  create_deck() %>% 
  sample_n(size = n) %>%
  select(report) %>% 
  pull()
}
```


### 1A)

```{r 1A, echo=FALSE}

# I first set the seed to 2. I then call my draw_card function with n = 4 and
# report = “name”.

set.seed(2)
draw_card(n = 4, report = "name")
```


### 1B)

```{r 1B, echo=FALSE}

# Now I set the seed to 3. I create a tibble called “hands” that draws a sample
# (without replacement) of 5 cards, 100 times. I then use map_lgl to create a
# column called “face” which tests whether there are any face cards (J, Q, K) in
# the hand, using an ifelse() condition. (I am sure there are more efficient
# ways to test for at least one face card within a draw, but here I end up doing
# it manually by checking each index of the draw.)

set.seed(3)
hands <- tibble(
  draw = map(1:100, ~ draw_card(n = 5, report = "value")),
  face = map_lgl(
    draw, 
    ~ ifelse(
      .[[1]] %in% c("J", "Q", "K") |
      .[[2]] %in% c("J", "Q", "K") |
      .[[3]] %in% c("J", "Q", "K") |
      .[[4]] %in% c("J", "Q", "K") |
      .[[5]] %in% c("J", "Q", "K"), 
      TRUE, 
      FALSE)
  )
)

# Finally, I use gt() to display the first 5 rows of the tibble. I slice for the
# first five rows, and then use the gt package to add a title and subtitle and
# relabel the columns as appropriate.

fivecards <- hands %>% 
  slice(1:5) %>% 
  gt() %>% 
  tab_header(
    title = "Hands of Five Cards",
    subtitle = "Checking for Face Values"
  ) %>%
  cols_label(
    draw = "Draw",
    face = "Face Cards?"
  )
fivecards
```


### 1C)

```{r 1C, echo=FALSE}

# I first set the seed to 4. Here I draw my own sample of 12 cards from the deck
# created by create_deck() and select just the name and points columns. I
# decided to directly use sample_n() with size = 12 to draw this sample rather
# than use the function I created earlier, draw_sample, in order to allow for
# selecting and viewing multiple columns from the deck tibble.

set.seed(4)
twelve_cards_once <- create_deck() %>% 
  sample_n(size = 12) %>% 
  select(name, points)

# Here I use gt() to display a table of all 12 sampled cards with card name and
# point value. I chose not to pipe directly from the previous code chunk to gt()
# so that I can successfully draw from twelve_cards_once, as a data frame, in
# 1E) later on.

twelve_cards_table <- twelve_cards_once %>% 
  gt() %>% 
  tab_header(
    title = "Sample of 12 Cards"
  ) %>% 
  cols_label(
    name = "Card Name",
    points = "Point Value"
  )
twelve_cards_table
```


### 1D)

```{r 1D, echo=FALSE}

# I call create_deck() to create the entire deck of cards and then call mean()
# within summarize() to find the average number of points. I have to first
# convert the entries in the points column to numeric values, in order to be
# able to apply the mean() function.

r1D <- create_deck() %>%  
  summarize(mean(as.numeric(points)))
```

The mean number of points in our entire deck is `r r1D`.


### 1E)

```{r 1E, echo=FALSE}

# I first set the seed to 5. Here I conduct bootstrapped resampling on the hand
# of 12 cards created in 1C). In sampling 1000 times, I have to sample with
# replacement so as to not get back the same hand of 12 cards every single time.
# I chose not to store these resamples in a tibble using map(), since doing so
# was giving me complications later on when I tried to plot the tibble.

set.seed(5)
bootstrap <- twelve_cards_once %>% 
  rep_sample_n(size = 12, reps = 1000, replace = TRUE)

# Now I prepare my bootstrap tibble for replicating the plot shown in the
# problem set instructions, which compares the original sample mean to the mean
# of the bootstrapped resamples. Here I group by "replicate" to group each
# sample together, and then use summarize() to calculate the mean of each of the
# bootstrapped samples.

bootstrap_mean <- bootstrap %>% 
  group_by(replicate) %>% 
  select(replicate, name, points) %>% 
  summarize(bootstrap_mean = mean(as.numeric(points)))

# Here I calculate the mean of the all bootstrapped sample means found above, in
# order to visualize the mean of the entire distribution in the plot later on

bootstrap_mean_overall <- bootstrap_mean %>% 
  summarize(bootstrap_mean_overall = mean(bootstrap_mean))

# Here I plot my bootstrap_mean tibble, with bootstrapped sample means on the
# x-axis. It took some playing around to settle on bins = 20, via some help on
# Zoom. I then use geom_vline() to add the two vertical lines with x-intercepts
# at the mean of bootstrapped samples and the mean of the entire original deck
# (as calculated in 1D)). Lastly, I apply theme_classic() to mimic the plot in
# the problem set instructions.

bootstrap_plot <- bootstrap_mean %>% 
  ggplot(aes(x = bootstrap_mean)) +
  geom_histogram(bins = 20) +
  labs(
    title = "Distribution of 1000 Bootstrapped Resamples",
    subtitle = "From original 12 card sample with mean 7.231",
    x = "Points",
    y = "Samples"
  ) +
  geom_vline(
    xintercept = bootstrap_mean_overall$bootstrap_mean_overall, 
    color = "lightblue"
  ) +
  geom_text(
    aes(x = 7.1, label = "Mean of Bootstrapped Samples", y = 51), 
    color = "lightblue",
    angle = 90
  ) +
  geom_vline(xintercept = 7.231, color = "pink") +
  geom_text(
    aes(x = 7.31, label = "Original Sample Mean", y = 51), 
    color = "pink",
    angle = 90
  ) +
  theme_classic()
bootstrap_plot
```

(The mean of the original sample (from 1D) is approximately 7.231, while the 
mean of the bootstrapped samples as found here is 7.20175.) Even after running 
1000 samples, the mean of the bootstrapped samples is slightly off due to the 
fact that the bootstrap samples are created by sampling with replacement, 
allowing for potentially drawing the same card(s) multiple times and thus 
skewing the mean.



### 1F)

```{r 1F, echo=FALSE}

# Here I create a function that takes in an input of level (e.g. 0.8, 0.9, 0.95,
# 0.99) and outputs corresponding “percentile confidence intervals” in the
# distribution of bootstrapped samples from 1E). I decided to create a function
# for this purpose in order to streamline the process of creating a tibble with
# level and interval columns, which I will need to create a gt table later on.

find_level <- function(level) {
  bootstrap_mean %>% 
    pull(bootstrap_mean) %>% 
    quantile(c((1 - level) / 2, (1 - level) / 2 + level)) %>% 
    round(digits = 1) %>% 
    rbind()
} 

# Here I create the aforementioned tibble with two columns, one for the
# confidence level and one for the corresponding interval of the distribution. I
# manually define the desired values in the "level" column for simplicity and
# use the function created above to define the values in the "interval" column.
# This is a bit more complicated and requires pasting the first element of the
# function output (the lower bound of the interval) and then the second element
# (the upper bound), with parentheses and separated by a comma. I do this four
# times within c() for the four different confidence levels.

perc_conf_int <- tibble( 
  level = c(0.8, 0.9, 0.95, 0.99),
  interval = c(
    paste("(", find_level(0.8)[[1]], ", ", find_level(0.8)[[2]], ")", sep = ""),
    paste("(", find_level(0.9)[[1]], ", ", find_level(0.9)[[2]], ")", sep = ""),
    paste("(", find_level(0.95)[[1]], ", ", find_level(0.95)[[2]], ")", sep = ""),
    paste("(", find_level(0.99)[[1]], ", ", find_level(0.99)[[2]], ")", sep = "")
  )
)

# Here I make a gt table using the tibble created above. As requested, I include
# the sample mean (the (non-bootstrapped) mean points for the original deck in
# 1D)) as a “source note” at the bottom of the table.

perc_conf_int_table <- perc_conf_int %>% 
  gt() %>% 
  tab_header(
    title = "Confidence Intervals for Average Point Value",
    subtitle = "Bootstrapped Resamples on a 12 Card Hand"
  ) %>% 
  cols_label(
    level = "Level",
    interval = "Interval"
  ) %>% 
  tab_source_note(source_note = "Original Sample Mean of 7.23")
perc_conf_int_table
```


### 1G)

```{r 1G, echo=FALSE}

# Here I write a function width_ci <- function(n, level) that draws a sample
# hand of n cards and creates a confidence interval at the appropriate
# confidence level. I draw from the earlier questions in this problem set to
# create the function: I first create a full deck and take a sample of size n
# from this deck, then bootstrap sample 1000 times with replacement from this
# deck using rep_sample_n(). I then group by each bootstrapped sample and find
# the mean of each sample. I then pull just the distribution of the bootstrapped
# sample means and, as above, use the percentile method to calculate the desired
# confidence interval. The final output of the function is the length of the
# interval, or the difference between the lower and upper bounds.

width_ci <- function(n, level) {
  sample <- create_deck() %>% 
    sample_n(size = n) %>% 
    rep_sample_n(size = n, reps = 1000, replace = TRUE) %>% 
    group_by(replicate) %>% 
    select(replicate, name, points) %>% 
    summarize(bootstrap_mean = mean(as.numeric(points))) %>% 
    pull(bootstrap_mean) %>% 
    quantile(c((1 - level) / 2, (1 - level) / 2 + level)) %>% 
    round(digits = 1)
  
  width = sample[[2]] - sample[[1]]
  
  width
}

# I set the seed to 6. Here I create a tibble which, for three different
# confidence levels (90%, 95%, 99%) and 51 different sample sizes (2:52) records
# the width of the bootstrapped confidence interval. Per the problem set
# instructions: I start with a sample of 2 cards since resampling from a sample
# of 1 card will always get the same card, leading to a confidence interval of
# 0. In addition to the sample_size column, I create one column for each of the
# three confidence levels, defining each column by mapping the output of
# width_ci to the sample_size which was inputted to the function. I then pivot,
# as hinted at in problem set instructions, to tidy up the data and prepare for
# plotting. As anticipated, the final tibble has 153 rows.

set.seed(6)
tibble <- tibble(
    sample_size = 2:52,
    "90" = map_dbl(sample_size, ~ width_ci(., level = 0.9)),
    "95" = map_dbl(sample_size, ~ width_ci(., level = 0.95)),
    "99" = map_dbl(sample_size, ~ width_ci(., level = 0.99))
  ) %>% 
  pivot_longer(
    names_to = "conf_level", 
    values_to = "width", 
    cols = -sample_size
  )

# Finally, I replicate the plot from the problem set instructions using the
# tibble created above.

plot <- tibble %>% 
  ggplot(aes(x = sample_size, y = width, color = conf_level)) +
  geom_point() +
  labs(
    title = "Width of Bootstrapped Confidence Intervals For Different Sample Sizes",
    subtitle = "Calculating the Mean Point Value from a Deck of Cards",
    x = "Sample Size",
    y = "Width of Confidence Interval\n (Percentile Method)",
    color = "Confidence Level"
  ) +
  theme_classic()
plot
```



## Question 2: Shiny

[link to Shiny app]


